\documentclass[english]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}

\usepackage[linesnumbered,ruled,vlined]{algorithm2e}

\usepackage{amsfonts}
\usepackage{amsmath}

\newcommand{\N}{\mathbb{N}}

\newtheorem{lemm}{Lemma}

\title{Matching mechanisms for kidney transplantations}
\author{Tristan François}

\begin{document}

\maketitle

\section{Two Simple Approaches}

\subsection*{Question 1}

\begin{algorithm}[H]
% \DontPrintSemicolon
\caption{Direct Donation}

\KwIn{A number $n$ of patient and, for all patients $i \in \N$, their set of compatible donors $K_i \subseteq [\![1, n]\!]$.}
\KwOut{A set of pairs donor-patient pairs $c$ and a waiting list $w$.}
\Begin{
$c = \emptyset$\;
$w = []$\;
\For{$i = 1$ \KwTo $n$}{
    \If{$i \in K_i$}{
        $c = c \cup \{(i,i)\}$\; 
    }
    \Else{
        $w$.add($i$)
    }
}
\Return{$c$, $w$}}

\end{algorithm}

The implementation in python is pretty straightforward. The python function takes as parameter an integer $n$ and an integer set array of size $n$. The use of python set allows to test the if condition in constant times. The only difference with pseudo-code is the use of a list rather than a set for the variable c. This choice was made to avoid the unnecessary heaviness of the set data structure, but does not change the complexity.

\subsection*{Question 2}
\begin{algorithm}[H]
    % \DontPrintSemicolon
    \caption{Greedy Matching}
    
    \KwIn{A number $n$ of patient, a strict priority list of the patients U and, for all patients $i \in \N$, their set of compatible donors $K_i \subseteq [\![1, n]\!]$ and their strict preference relation $P_i$ over $K_i \cup \{k_i, w\}$. The priority list U starts with the patient with the highest priority and goes decreasingly to the lowest priority.}
    \KwOut{A set of pairs donor-patient pairs $c$ and a waiting list $w$.}
    \Begin{
    $c = \emptyset$\;
    $w = []$\;
    $matched = []$\;
    \For{$i = 1$ \KwTo $n$}{
        matched.add(False)\;
    }
    \Return{$c$, $w$}}
    
    \end{algorithm}

\section{Efficient stategy-proof exchange mechanism}

\subsection*{Question 3}

Let $(k_1,t_1)$ be a pair of donor-patient and assume there is no cycle. Consider the chain starting from $(k_1,t_1)$. Since there is a finite number $n$ of donor-patient pairs and there is no cycle, the chain cannot be infinite. Finally, since the only way for a chain to stop is that $w$ belong to the chain, $(k_1,t_1)$ is indeed a tail of a $w$-chain.

Thus either there exists a cycle, or each pair is the tail of some $w$-chain.


\end{document}